---
title: "Eating Out"
author: "your name here"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

According to this barchart, we can see by looking at it that there are about 80% white people eating out, about 70% black people eating out, and a little over 70% of other races that eat out. Even though there is no dramatic difference, white people ate out the most out of the given races.


```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

After obtaining the numerical results, we can see that 83.11% of white people, 69% of black people, and 72% of other people eat out. This confirms that white people ate out the most overall.


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

```{r}
fisherXY(mydata$race,mydata$eatout,
printAll = TRUE)
```

According to the fisherXY test, we have been given a p-value of 1.183*e-05 which is a very small number and indicates that when the fisherXY test was ran, they found that black and white were statistically different. When the test is run on white and other, the p-value is .007. Therefore, this tells us that white is different than others and white is different from black. The p-value for black and others is 0.99 which is not a small value. This then tells us that black and others are not different. 


In conclusion, we were able to look at barplots, numerical results, and the fisherXY test for the three variables. This has allowed us to come to the conclusion that black and others are not the different but, white and others as well as white and black are different. This can be achieved by running a fisherXY test and analyzing the p-values.

